Transforming Trash as an Artistic Act

### 2016-01-17 main.tex
errors
Former-commit-id: 15772ce8859d48cb14d18f35bbe189c5237d715a
reorganization
Former-commit-id: e5cf9d1ed889ae9676d7eb070201bb31780d7a02
reorganization
Former-commit-id: 25c0a96c39ba879be0bc5c822db2ca3bbc11d003
ESBE format fixes
Former-commit-id: 1288a0dfad49d9c17475ca7c59ee6ac980212352
Proof reading
Former-commit-id: d835c4ff57c702c8f90dae1816f3609db8679019

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,left=40.1mm,top=24.1mm,right=25.1mm,bottom=36mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc,title]{appendix}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{afterpage}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

@@

@@

\usepackage{xpatch}

\xpatchbibmacro{date+extrayear}{%
  \printtext[parens]%
}{%
  \setunit*{\addperiod\space}%
  \printtext%
}{}{}

% Adding extra space between paragraphs
\setlength{\parskip}{\baselineskip}

% Quote spacing
\expandafter\def\expandafter\quote\expandafter{\quote\singlespacing}

% To align left todos
\reversemarginpar

% Chapter titles
\usepackage{titlesec}
\titleformat{\chapter}[display]
        {\normalfont\fontsize{14pt}{12pt}\centering\bfseries}{\MakeUppercase{\chaptertitlename}\  \thechapter}{2\baselineskip}{\uppercase}
\titleformat*{\section}{\bfseries\fontsize{12pt}{12pt}}
\titleformat*{\subsection}{\bfseries\fontsize{12pt}{12pt}}

% Chapter title spacing
\titlespacing{\chapter}{0pt}{9mm}{3\baselineskip}

% Epigraph setup
\setlength{\epigraphwidth}{.65\textwidth}
\setlength{\epigraphrule}{0pt}

@@

% RENAMING CHAPTER TITLES
\addto\captionsenglish{%
  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
  \renewcommand{\bibname}{\MakeUppercase{Bibliography}}%
}

@@

%****************************************
% COVER
\begin{titlepage}
    \begin{center}

        \singlespacing

@@

        \vspace*{25mm}
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        \vspace*{4\baselineskip}
        Graduate School of Economics and Social Sciences\\
        of\\
		İhsan Doğramacı Bilkent University\\
		\vspace*{2\baselineskip}
        by\\
       	\vspace*{2\baselineskip}
        MUSTAFA İLHAN\\
        \vspace*{3\baselineskip}
        In Partial Fulfilment of the Requirements for the Degree of\\
		MASTER OF FINE ARTS\\
        \vspace{\baselineskip}
        in\\
        \vspace{\baselineskip}
        THE DEPARTMENT OF\\
        COMMUNICATION AND DESIGN\\
       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
        ANKARA\\
        \vspace{\baselineskip}
        January 2016
	\end{center}
\clearpage
%........................................

%****************************************
% APPROVAL PAGE
\clearpage
\thispagestyle{empty}
\singlespacing
\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\

@@

%****************************************
% ENGLISH ABSTRACT
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\doublespacing
\begin{center}
	\vspace*{7mm}
	\MakeUppercase{Abstract}\\
    \vspace{\baselineskip}
    TRANSFORMING TRASH AS AN ARTISTIC ACT\\
    İlhan, Mustafa\\
    M.F.A., Department of Communication and Design\\
    Supervisor: Assist. Prof. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    January 2016
\end{center}
\singlespacing
\par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century. This approach has broken the existing rules and extended the language of art in an unprecedented way. After that point, trash has found a place in the work of artists.

The purpose of this study is to discuss usage of trash in the context of art. The role of art is questioned in the transformation of discarded items. This thesis follows the discussions on the place of trash in culture and theories of trash. Then approaches and methodologies of artists who use discarded materials in their works are explored. It is questioned that why and how they use discarded materials and how their artworks can be understood regarding theoretical and cultural aspects.

Within this framework, thesis project argues that it is possible to see the process of transforming trash as an artistic act. In the scope of the project, discarded papers are collected with the help people and transformed to notebooks. Progress and collected items are recorded on a website. Notebooks are installed in non-conventional locations such as library desks and computer labs in order to invite people to use trash again.

@@

%****************************************
% TURKISH ABSTRACT
\thispagestyle{plain}
\selectlanguage{turkish}
\phantomsection
\addcontentsline{toc}{chapter}{ÖZET}
\doublespacing
\begin{center}
	\vspace*{9mm}
	\MakeUppercase{Özet}\\
    \vspace{\baselineskip}
    \MakeUppercase{Sanatsal Bir Eylem Olarak Atığı Dönüştürme}\\
    İlhan, Mustafa\\
    Yüksek Lisans, İletişim ve Tasarım Bölümü\\
    Tez Yöneticisi: Yrd. Doç. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    Ocak 2016
\end{center}
\singlespacing
\par Sanat işlerinde sanat dışı nesnenin kullanımı 20. yüzyılın başına kadar takip edilebilmektedir. Bu yaklaşım var olan kuralları yıkmış ve sanatın dilini eşi görülmemiş bir biçimde genişletmiştir. Bu noktadan sonra atık sanatçıların işlerinde yer bulmuştur.

Bu çalışmanın amacı sanatsal bağlamda atığın kullanımını tartışmaktır. Atık ürünlerin dönüştürülmesinde sanatın rolü işlerinde atık maddeleri kullanan sanatçıların yaklaşımları ve yöntemleri üzerinden sorgulanmıştır. Çöpün kültürel ve kuramsal olarak nasıl ele alındığı araştırılmıştır. Sanatçıların neden ve nasıl atık malzemeleri kullandıkları ve işlerinin kültürel ve kuramsal açılardan nasıl anlaşılabileceği sorgulanmıştır.

Bu çerçevede, tez projesi atığı dönüştürme sürecinin bir sanatsal eylem olarak görülebileceğini savunmaktadır. Proje kapsamında atık kağıtlar insanların yardımıyla toplanıp not defterlerine dönüştürülmüştür. Süreç ve toplanan ürünler bir web sitesinde kayıt altına alınmıştır. İnsanların atığı tekrar kullanmaya davet etmek amacıyla defterler sık ziyaret edilen kütüphane, bilgisayar laboratuvarı gibi ortak kullanım alanlarına yerleştirilmiştir.

%\par \comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir. Ya da en azından proje kapsamında üretilen işin. Ya da bu bağlamda ele alınabileceği iddia edilmektedir.}

@@

%\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır. Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır. Bu defter hakim sistemin dışındaki mekanlarda konulmuştur. (kamusal ortak alan)}

%\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.). Beraberinde pek çok akım ve üretim biçimini tetiklemiştir. Hem sanatın dili genişledi hem de objeler sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı. Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır. Çöpün nasıl sanatta yer bulduğu incelenmiştir.}

%Çöp ve sanatsal eylem birlikte alınarak incelenmiştir. Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır. Teoriler ve methodlar ele alınmıştır. Çöpün ne olduğu sorgulanmaktadır ve çöpe yeni bir bakış açısı kazandırmak amaçlanmaktadır.

%Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır. Bu atık maddeler dönüştürülerek defter yapılmıştır. Renk, doku, biçim ve üretim yöntemi ile endüstriyel defterlere alternatif bir yaklaşım olması amaçlanmıştır. Bu defterler insanların ulaşabileceği belirli mekanlara dağıtılmıştır (yerleştirilmiştir). Mekanlar da aynı şekilde eleştirel bakış açısına açık yerler arasından seçilmiştir. Alternatif bir ortam sunan mekanlar seçilmiştir. Defterlerin mekanla belirli bir anlamsal ilişki içine girmesi amaçlanmıştır. Bu proje sonunda dönüştürülen şeylerin aynı zamanda dönüşütüğü şeyi de başka bir şeye dönüştürdüğü anlaşılmaktadır. Çöpe olan bakış açısının dönüştürülmesi amaç edilmiştir.

@@

%****************************************
% ACKNOWLEDGMENTS
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\doublespacing
\begin{center}
	\vspace*{7mm}
	\MakeUppercase{ACKNOWLEDGMENTS}\\
    \vspace{3\baselineskip}
\end{center}
\par First and foremost, I would like to thank to my thesis supervisor Assist. Prof. Dr. Ersan Ocak for his endless patience, support and encouragement through the whole progress. He contributed in every way he can and guided me through the development of this thesis with his immense knowledge. I also would like to thank the rest of my thesis committee; Prof. Dr. Mehmet Yılmaz and Instructor Ekin Kılıç for their valuable contributions and insightful comments on the issues of this thesis.

@@

I would like to thank my bosses and colleagues from Mobilus; Özgür Deniz Önür, Yağız Yaşaroğlu, Ekin Dino, Ayşegül Yaşaroğlu, Süleyman Yıldız and Aytaç Kocaman for their support, trust and sharing their discard with me.

I am grateful to M. Elgin Akpınar, Nihan Özdemirler, M. Cem B. Üstündağ, B. Ceren D. Üstündağ, Ayşenur Durgut, Emrah Şamdan, Duygu Ç. Şamdan, Ali from METU Technopolis İş Bank Office, Aykut from Modshifters and Varuna Gezgin for collecting and sharing their discard with me.

Lastly and mostly, I would like to thank my family for their love, trust and support from the very beginning of this work. 
\clearpage
%........................................

@@

\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % dots for chapters
\renewcommand{\cfttoctitlefont}{\normalfont\MakeUppercase\hfil}
\renewcommand\cftchapfont{\mdseries}
\renewcommand\cftchappagefont{\mdseries}
\renewcommand{\cftchappresnum}{CHAPTER\space}
\renewcommand{\cftchapaftersnum}{:}

\setlength{\cftbeforetoctitleskip}{19mm}
\setlength{\cftaftertoctitleskip}{3\baselineskip}
\setlength{\cftchapnumwidth}{7em}
%\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}

@@

\renewcommand{\cftloftitlefont}{\normalfont\MakeUppercase\hfil}
\renewcommand{\cftfigaftersnum}{.}

\setlength{\cftbeforeloftitleskip}{19mm}
\setlength{\cftafterloftitleskip}{3\baselineskip}
\setlength{\cftbeforefigskip}{\cftbeforechapskip}

@@

%****************************************
% CHAPTERS
\include{chapter1_reduced}
\include{chapter2_reduced}
\include{chapter3_reduced}
\include{chapter4_reduced}
\include{chapter5}
%........................................

% TODO yıl olayını düzeltmeli
% Bibliographyden sonra 4 boşluk olmalı?

%****************************************
% BIBLIOGRAPHY
\nocite{*} % Add all references
\phantomsection
\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
\bibliographystyle{apacite}
\begin{singlespace}
\setlength{\bibsep}{2\itemsep}
\bibliography{literature}
\end{singlespace}
\clearpage
%........................................

%****************************************
% APENDICES
%\appendix

%\addtocontents{toc}{\cftpagenumbersoff{chapter}} 
%\chapter*{APPENDICES}
%\addtocontents{toc}{\protect\contentsline {chapter}{APPENDICES}{}{}}

%\addtocontents{toc}{\cftpagenumberson{chapter}}

%\makeatletter
%\addtocontents{toc}{\let\protect\l@chapter\protect\l@section}
%\makeatother

%\include{appendix_glossary}
%\include{appendix_materials}
%\include{appendix_project}
%........................................

>>>>

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,left=41.2mm,top=25.2mm,right=24.2mm,bottom=35mm]{geometry} % left: 40mm, top: 25mm, right: 25mm, bottom: 25mm
\usepackage{epigraph}
\usepackage{graphicx}
\usepackage{float}
\usepackage[font={footnotesize,bf}]{caption}
\usepackage[font={footnotesize,bf}]{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc,title]{appendix}
\usepackage{afterpage}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}
\usepackage{url}
\usepackage{indentfirst}

% Turning off all figures, required for turnitin upload
% Remove the next two lines if you want the figures at their place
\usepackage[figuresonly,nolists,nomarkers]{endfloat}
\renewcommand{\processdelayedfloats}{}

% Same fonts for URL
\AtBeginDocument{\urlstyle{APACsame}}

@@

%****************************************
% SPACING

% Adding extra space between paragraphs
\setlength{\parskip}{0.5\baselineskip}
%........................................

%****************************************
% BIBLIOGRAPHY

@@

% Removing parentheses around year in bibliography
\AtBeginDocument{
\renewcommand{\BBOP}{}
\renewcommand{\BBCP}{}
}

% Adding ":" character before page number
\bibpunct[: ]{(}{)}{:}{a}{,}{~}
%........................................

%****************************************
% BLOCK QUOTES

% Spaces before and after block quotes
\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\vspace{-\baselineskip}}
\AtEndEnvironment{quote}{\vspace{-\baselineskip}}

% Spaces before and after block quotes, indentation
\renewcommand{\quote}{\list{}{\rightmargin=4em\leftmargin=4em}\item\relax}

% Spacing
\expandafter\def\expandafter\quote\expandafter{\quote\singlespacing}
%........................................

%****************************************
% CHAPTERS

% Chapter titles
\usepackage{titlesec}
\titleformat{\chapter}[display]
        {\normalfont\fontsize{14pt}{14pt}\centering\bfseries}{\MakeUppercase{\chaptertitlename}\  \thechapter}{2\baselineskip}{\uppercase}
\titleformat*{\section}{\bfseries\fontsize{12pt}{12pt}}
\titleformat*{\subsection}{\bfseries\fontsize{12pt}{12pt}}

% Chapter title spacing
\titlespacing{\chapter}{0pt}{13mm}{3\baselineskip} % Centered, Top: 50mm, Next: 3 line after
% Bibliography title spacing
\titlespacing*{name=\chapter,numberless}{0pt}{16mm}{4\baselineskip} % Centered, Top: 50mm, Next: 4 line after

% RENAMING CHAPTER TITLES
\addto\captionsenglish{%
  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
  \renewcommand{\bibname}{\MakeUppercase{Select Bibliography}}%
}
%........................................

%****************************************
% EPIGRAPH

% Epigraph setup
\setlength{\epigraphwidth}{.65\textwidth}
\setlength{\epigraphrule}{0pt}
%........................................

@@

@@

%****************************************
% COVER
\begin{titlepage}
\singlespacing
    \begin{center}

@@

        \vspace*{25mm}
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        \vspace*{4\baselineskip}
        Graduate School of Economics and Social Sciences\\
        of\\
		İhsan Doğramacı Bilkent University\\
		\vspace*{2\baselineskip}
        by\\
       	\vspace*{2\baselineskip}
        MUSTAFA İLHAN\\
        \vspace*{3\baselineskip}
        In Partial Fulfilment of the Requirements for the Degree of\\
		MASTER OF FINE ARTS\\
        \vspace{\baselineskip}
        in\\
        \vspace{\baselineskip}
        THE DEPARTMENT OF\\
        COMMUNICATION AND DESIGN\\
       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
        ANKARA\\
        \vspace{\baselineskip}
        January 2016

	\end{center}
\clearpage
%........................................

%****************************************
% APPROVAL PAGE
\clearpage
\thispagestyle{empty}
%\singlespacing
%\doublespacing
\noindent I certify that I have read this thesis and have found that it is fully adequate, in scope and in quality, as a thesis for the degree of Master of Fine Arts in Media and Design.\\

@@

%****************************************
% ENGLISH ABSTRACT
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\doublespacing
\begin{center}
	\vspace*{13mm} % Top: 50mm
	{\fontsize{14pt}{14pt}\selectfont \textbf{\MakeUppercase{Abstract}}}\\
    \vspace{\baselineskip}
    TRANSFORMING TRASH AS AN ARTISTIC ACT\\
    İlhan, Mustafa\\
    M.F.A., Department of Communication and Design\\
    Supervisor: Assist. Prof. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    January 2016
\end{center}
%\singlespacing
\par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century. This approach has broken the existing rules and extended the language of art in an unprecedented way. After that point, trash has found a place in the work of artists.

The purpose of this study is to discuss usage of trash in the context of art. This thesis questions the role of art in the transformation of discarded items through the approaches and methods of artists who use discarded materials in their works. It examines why and how artists use discarded materials and how their artworks can be understood regarding theoretical and cultural aspects. This study is supported by theoretical and philosophical ideas about garbage.

Within this framework, thesis project argues that it is possible to see the process of transforming trash as an artistic act. In the scope of the project, discarded papers are collected with the help people and transformed to notebooks. Progress and collected materials are recorded on a website. Notebooks are installed in non-conventional art spaces such as library desks and computer labs that are frequently visited common places in order to invite people to use trash again.

@@

%****************************************
% TURKISH ABSTRACT
\thispagestyle{plain}
\selectlanguage{turkish}
\phantomsection
\addcontentsline{toc}{chapter}{ÖZET}
\doublespacing
\begin{center}
	\vspace*{13.5mm} % Top: 50mm
	{\fontsize{14pt}{14pt}\selectfont \textbf{\MakeUppercase{Özet}}}\\
    \vspace{\baselineskip}
    \MakeUppercase{Sanatsal Bir Eylem Olarak Atığı Dönüştürme}\\
    İlhan, Mustafa\\
    Yüksek Lisans, İletişim ve Tasarım Bölümü\\
    Tez Yöneticisi: Yrd. Doç. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    Ocak 2016
\end{center}
%\singlespacing
\par Sanat işlerinde sanat dışı nesnenin kullanımı 20. yüzyılın başına kadar takip edilebilmektedir. Bu yaklaşım var olan kuralları yıkmış ve sanatın dilini eşi görülmemiş bir biçimde genişletmiştir. Bu noktadan sonra atık sanatçıların işlerinde yer bulmuştur.

Bu çalışmanın amacı sanatsal bağlamda atığın kullanımını tartışmaktır. Atık ürünlerin dönüştürülmesinde sanatın rolü, işlerinde atık maddeleri kullanan sanatçıların yaklaşımları ve yöntemleri üzerinden sorgulanmaktadır. Sanatçıların neden ve nasıl atık malzemeleri kullandıkları ve işlerinin kültürel ve kuramsal açılardan nasıl anlaşılabileceği araştırılmaktadır. Bu çalışma çöpe dair kuramsal ve felsefi fikirler ile desteklenmektedir.

Bu çerçevede, tez projesi atığı dönüştürme sürecinin bir sanatsal eylem olarak görülebileceğini savunmaktadır. Proje kapsamında atık kağıtlar insanların yardımıyla toplanıp not defterlerine dönüştürülmüştür. Süreç ve toplanan malzemeler bir web sitesinde kayıt altına alınmıştır. İnsanları atığı tekrar kullanmaya davet etmek amacıyla, defterler geleneksel sanat mekanı olarak kabul edilmeyen kütüphane, bilgisayar laboratuvarı gibi sık ziyaret edilen ortak kullanım alanlarına yerleştirilmiştir.

% Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir. Ya da en azından proje kapsamında üretilen işin. Ya da bu bağlamda ele alınabileceği iddia edilmektedir.

@@

% Tez dahilinde geliştirilen proje ile çöpten dönüştürülerek üretilen defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır. Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır. Bu defter hakim sistemin dışındaki mekanlarda konulmuştur. (kamusal ortak alan)

% Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir (ve çöpün sanat işlerinden kullanılması bu bağlamda incelenebilmektedir.). Beraberinde pek çok akım ve üretim biçimini tetiklemiştir. Hem sanatın dili genişledi hem de objeler sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı. Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır. Çöpün nasıl sanatta yer bulduğu incelenmiştir.

% Çöp ve sanatsal eylem birlikte alınarak incelenmiştir. Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır. Teoriler ve methodlar ele alınmıştır. Çöpün ne olduğu sorgulanmaktadır ve çöpe yeni bir bakış açısı kazandırmak amaçlanmaktadır.

% Tez dahilinde geliştirilen proje için insanlar örgütlenerek farklı mekanlardan farklı tiplerde atık kağıtlar toplanmıştır. Bu atık maddeler dönüştürülerek defter yapılmıştır. Renk, doku, biçim ve üretim yöntemi ile endüstriyel defterlere alternatif bir yaklaşım olması amaçlanmıştır. Bu defterler insanların ulaşabileceği belirli mekanlara dağıtılmıştır (yerleştirilmiştir). Mekanlar da aynı şekilde eleştirel bakış açısına açık yerler arasından seçilmiştir. Alternatif bir ortam sunan mekanlar seçilmiştir. Defterlerin mekanla belirli bir anlamsal ilişki içine girmesi amaçlanmıştır. Bu proje sonunda dönüştürülen şeylerin aynı zamanda dönüşütüğü şeyi de başka bir şeye dönüştürdüğü anlaşılmaktadır. Çöpe olan bakış açısının dönüştürülmesi amaç edilmiştir.

@@

%****************************************
% ACKNOWLEDGMENTS
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\doublespacing
\begin{center}
	\vspace*{13mm}
	{\fontsize{14pt}{14pt}\selectfont \textbf{\MakeUppercase{ACKNOWLEDGMENTS}}}\\
    \vspace{3\baselineskip}
\end{center}
\par First and foremost, I would like to thank to my thesis supervisor Assist. Prof. Dr. Ersan Ocak for his endless patience, support and encouragement through the whole progress. He contributed in every way he can and guided me through the development of this thesis with his immense knowledge. I also would like to thank the rest of my thesis committee; Prof. Dr. Mehmet Yılmaz and Instructor Ekin Kılıç for their valuable contributions and insightful comments on the issues of this thesis.

@@

I would like to thank my bosses and colleagues from Mobilus; Özgür Deniz Önür, Yağız Yaşaroğlu, Ekin Dino, Ayşegül Yaşaroğlu, Süleyman Yıldız and Aytaç Kocaman for their support, trust and collecting their discard for the thesis project.

I am grateful to M. Elgin Akpınar, Nihan Özdemirler, M. Cem B. Üstündağ, B. Ceren D. Üstündağ, Ayşenur Durgut, Emrah Şamdan, Duygu Ç. Şamdan, and Koray Benli for their valuable friendship, and also Ali from METU Technopolis İş Bank Office, Aykut from Modshifters, and Varuna Gezgin for collecting discarded materials for the thesis project.

Lastly and mostly, I would like to thank my family for their love, trust and support from the very beginning of this study. 
\clearpage
%........................................

@@

\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % dots for chapters
\renewcommand{\cfttoctitlefont}{\MakeUppercase\hfil\bfseries\fontsize{14pt}{14pt}\selectfont}
\renewcommand\cftchapfont{\mdseries}
\renewcommand\cftchappagefont{\mdseries}
\renewcommand{\cftchappresnum}{CHAPTER\space}
\renewcommand{\cftchapaftersnum}{:}

\setlength{\cftbeforetoctitleskip}{20mm}
\setlength{\cftaftertoctitleskip}{3\baselineskip}
\setlength{\cftchapnumwidth}{7em}
%\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}

@@

\renewcommand{\cftloftitlefont}{\MakeUppercase\hfil\bfseries\fontsize{14pt}{14pt}\selectfont}
\renewcommand{\cftfigaftersnum}{.}

\setlength{\cftbeforeloftitleskip}{20mm}
\setlength{\cftafterloftitleskip}{3\baselineskip}
\setlength{\cftbeforefigskip}{\cftbeforechapskip}

@@

%****************************************
% CHAPTERS
\include{chapter1_final}
\include{chapter2_reduced}
\include{chapter3_reduced}
\include{chapter4_reduced}
\include{chapter5}
%........................................

%****************************************
% BIBLIOGRAPHY
\nocite{*} % Add all references
\phantomsection
\addcontentsline{toc}{chapter}{SELECT BIBLIOGRAPHY}
\bibliographystyle{apacite}
\begin{singlespace}
\setlength{\bibsep}{2\itemsep}
\bibliography{literature}
\end{singlespace}
\clearpage
%........................................

%****************************************
% APENDICES
\appendix
\phantomsection
\addtocontents{toc}{\cftpagenumbersoff{chapter}} 
\chapter*{APPENDICES}
\addtocontents{toc}{\protect\contentsline {chapter}{APPENDICES}{}{}}

\addtocontents{toc}{\cftpagenumberson{chapter}}

\makeatletter
\addtocontents{toc}{\let\protect\l@chapter\protect\l@section}
\makeatother

%\include{appendix_glossary}
\include{appendix_materials}
\include{appendix_project}
%........................................
